# National and international events, days, observances and awards

## Days, year, decades and national and international observances

### Day observances

```{r day-observances}
# retrieved: April 6, 2020
# read_html("https://en.wikipedia.org/wiki/List_of_minor_secular_observances") %>% 
#   html_table(fill = T) %>% 
#   .[3:(3+11)] %>% 
#   map_dfr(function(x)as_tibble(x, .name_repair = "universal")) %>% 
#   write_csv("./data/minor_secular_observances_international_days.csv", na = "")

# todo: remove square bracket citations
read_csv("./data/world_minor_secular_observances_international_days.csv") %>% 
  mutate_all(list(~str_remove_all(., pattern = "\\[\\d*\\]"))) %>%
  knitr::kable(booktabs = TRUE, caption = "List of minor secular observances (Days)", longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped") %>%
  kableExtra::column_spec(column = 1:3, width = c("8em", "18em", "10em"))
```


### International year observances

```{r international-years}
# retrieved: April 6, 2020
read_csv("./data/world_minor_secular_observances_international_year.csv") %>% 
  mutate_all(list(~str_remove_all(., pattern = "\\[\\d*\\]"))) %>%
  knitr::kable(booktabs = TRUE, caption = "List of minor secular observances (Years)", longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped") %>% 
  kableExtra::column_spec(column = 1:2, width = c("8em", "22em"))

```

### Decade observances

```{r international-decades}
# retrieved: April 6, 2020
read_csv("./data/world_minor_secular_observances_international_decades.csv") %>% 
  mutate_all(list(~str_remove_all(., pattern = "\\[\\d*\\]"))) %>%
  knitr::kable(booktabs = TRUE, caption = "List of minor secular observances (Decades)", longtable = TRUE) %>%
  kableExtra::kable_styling(latex_options = "striped") %>% 
  kableExtra::column_spec(column = 1:3, width = c("8em", "20em", "10em"))

```

**Other observances**

- Greenery Day -- May 4
- Remembrance of the Dead -- May 4
- World Wide Day of Genital Autonomy -- May 7
- Teacher's Day -- May 8
- Victory in Europe Day -- May 8
- Military Spouse Day -- May 11
- Mother's Day -- May 13
- International Day of Families -- May 15
- Norwegian Constitution Day -- May 17
- World Inflammatory Bowel Disease (IBD) Day - May 19
- Labour Day (Jamaica) -- May 23
- World Orienteering Day -- May 24
- African Liberation Day -- May 25
- International Missing Children's Day -- May 25
- World Multiple Sclerosis Day -- May 25
- Menstrual Hygiene Day -- May 28
- Memorial Day -- last Monday of May

- Queen's Official Birthday -- first, second or third Saturday in June
- National Cancer Survivors Day (US) -- first Sunday of June
- Republic Day (Italy) -- June 2
- Danish Constitution Day -- June 5
- Coral Triangle Day -- June 9
- Independence Day (Philippines) -- June 12
- Juneteenth -- June 19 and/or third Saturday of the month
- World Hydrography Day -- June 21
- World Music Day -- June 21
- Fête Nationale du Québec -- June 24
- Tau Day -- June 28
- World Wide Knit in Public Day -- second Saturday in June

- National Doctors' Day (India) -- July 1
- Chartered Accountants' Day (India) -- July 1
- Tynwald Day (Isle of Man) -- July 5
- The Twelfth (Northern Ireland) -- July 12
- Kargil Vijay Diwas -- July 26
- Comic Sans Day - First Friday of July

- International Beer Day -- first Friday of August
- Emancipation Day (Jamaica) -- August 1
- Yorkshire Day -- August 1
- Friendship Day -- first Sunday of August
- Independence Day (Jamaica) -- August 6
- National Day (Singapore) -- August 9
- International Youth Day -- August 12
- International Lefthanders Day -- August 13
- Youm-e-Azadi (Pakistan Independence Day) -- August 14
- National day of mourning (Bangladesh) -- August 15
- Independence Day (India) -- August 15
- Victory over Japan Day (UK) -- August 15
- Bennington Battle Day -- August 16
- Indonesian Independence Day -- August 17
- World Mosquito Day -- August 20
- Indian Akshay Urja Day -- August 20
- International Day for the Remembrance of the Slave Trade and its Abolition -- August 23
- European Day of Remembrance for Victims of Stalinism and Nazism -- August 23
- Women's Equality Day -- August 26
- National Sports Day -- August 29
- Hari Merdeka (Malaysia Independence Day) -- August 31
- Friendship Day -- First Sunday of August

- Victory over Japan Day (US) -- September 2
- Skyscraper Day -- September 3
- Teachers' Day (India) -- September 5
- Defense Day (Pakistan) -- September 6
- Brazilian Independence Day -- September 7
- World Physical Therapy Day -- September 8
- Patriot Day -- September 11
- Onam (Kerala, India) -- September 4, 2017
- Hindi Day -- September 14
- Engineer's Day (India) -- September 15
- Start of Mexican Independence Day -- September 16
- Malaysia Day -- September 16
- World Car Free Day -- September 22
- Heritage Day (South Africa) -- September 24
- Botswana Day -- September 30
    
- World Habitat Day -- first Monday of October
- World Ballet Day -- a day in the first week of October
- World Sight Day -- second Thursday of October
- International Day of Older Persons -- October 1
- International Coffee Day -- October 1
- World Vegetarian Day -- October 1
- Gandhi Jayanthi -- October 2
- International Day of Non-Violence -- October 2
- German Unity Day -- October 3
- Stevie Ray Vaughan Day (Austin, Texas, US) -- October 3
- World Animal Day -- October 4
- World Teachers' Day -- October 5
- German-American Day -- October 6
- National Poetry Day (Britain) -- October 6
- World Post Day -- October 9
- World Mental Health Day -- October 10
- Fiji Day (Fiji) - October 10
- Coming Out Day -- October 11
- Fiesta Nacional de España -- October 12
- World Standards Day -- October 14
- Pregnancy and Infant Loss Remembrance Day -- October 15
- Global Handwashing Day -- October 15
- World Students' Day -- October 15
- World Food Day -- October 16
- International Day for the Eradication of Poverty -- October 17
- World Osteoporosis Day -- October 20
- Trafalgar Day (United Kingdom) -- October 21
- Mole Day -- October 23
- United Nations Day -- October 24
- Intersex Awareness Day -- October 26
- Labour Day (New Zealand) -- fourth Monday in October
- National Cat Day (US) -- October 29
- Halloween -- October 31
- Reformation Day -- October 31
- World Ballet Day -- a day during the first week in October
    
- Kerala Piravi -- November 1
- World Vegan Day -- November 1
- All Saints' Day -- November 1
- All Souls' Day -- November 2
- Guy Fawkes Day -- November 5
- Intersex Day of Remembrance -- November 8
- Iqbal Day -- November 9
- Armistice Day (also Remembrance Day) -- November 11
- National Independence Day (Poland) -- November 11
- World Pneumonia Day -- November 12
- World Kindness Day -- November 13
- World Diabetes Day -- November 14
- Children's Day (some countries) -- November 14
- International Day for Tolerance -- November 16
- World Prematurity Day -- November 17
- International Men's Day -- November 19
- World Toilet Day -- November 19
- Citizen's Day -- November 19
- Universal Children's Day -- November 20
- Transgender Day of Remembrance -- November 20
- World Television Day -- November 21
- Thanksgiving -- November 23
- International Day for the Elimination of Violence against Women -- November 25
- Law Day (India) -- November 26
- National Milk Day (India) -- November 26
- Constitution Day (India) -- November 26
- Cities for Life Day -- November 30
- World Philosophy Day -- third Thursday in November

- International Volunteer Day -- December 5
- Sinterklaas -- December 5 / 6
- Independence Day (Finland) -- December 6
- Feast of the Immaculate Conception -- December 8
- Bahrain National Day -- December 16
- International Tea Day -- December 15
- Day of Reconciliation -- December 16
- International Day to End Violence Against Sex Workers - December 17
- Christmas Eve -- December 24
- Christmas Day -- December 25
- Good Governance Day (India) -- December 25
- Quaid-e-Azam Day -- December 25
- Boxing Day -- December 26
- Kwanzaa -- December 26 to January 1
- Benazir Bhutto Memorial Day (Karachi, Pakistan) -- December 27
- New Year's Eve -- December 31
- Purnima Sukla Paksha -- full moon day -- December

**Some important days for Nepal**

- Loktantra Day: Baisakh 11
- Ganatantra Day: Jestha 15
- NARC Day: May 8
- National Rice Day: Ashad 15
- Cooperative Day: Chaitra 20

## Events and programmes

### Nepal Investment Summit

Nepal hosted 3rd edition of Nepal Investment Summit on March 29-30, 2019 in the Kathmandu in an effort to further enhance Nepal's standing as a promising investment destination and to build on the recent encouraing developments. The 2nd summit was held in 2017, while the first one was held in 1992. 

Major Outcomes of Investment Summit, 2019

- Nepal Investment Summit 2019 has reportedly witnessed signing of 15 new deals and MoUs for new projects in Nepal
- Besides, the country has also received proposals, 17 applications for 10 other projects presented as part of the Summit
- Transport, hydropower, hospital, airport, convention center and agriculture infrastructure were among areas that received investment proposals
- India, Vietnam, United States, South Korea, China, Britain were among countries that represented participating investors
- International Finance Corporation, World Bank Group, Asian Development Bank, Multilateral Investment Guarantee Agency, were among the key multilateral donor agencies entered into separate investment and cooperation deals during the summit
- One of the world's largest solar development company SkyPower announced a new partnership with Nepal's Chaudhary Group for a 600-MW capacity renewable solar energy projects.
- PM and Finance Minister Khatiwada held 30 side-line bilateral meetings with investors and delegates as part of the Summit
- More than 1300 participants and around 735 foreign delegates from more 300 companies attended the Summit


The government, in an effort to attract foreign investors, has introduced three vital legislations—Foreign Investment and Technology Transfer Act, Public-Private Partnership and Investment Act, and Special Economic Zone Act (First Amendment).

### Nepal Infrastructure Summit

Nepal Infrastructure Summit (NIS) 2014, organized by CNI in collaboration with Government of Nepal and YCNC, with the theme "Accelerating Investment in Infrastructure" was 1st ever summit organized of its kind in Nepal. The Summit was successful as it was able to deliver high attendance, important and high-rated keynote speech, excellent speakers and panelists who knew their subject, well facilitated dialogue sessions, a great venue for networking and the presence of aspiring young participants.

The Summit provided a platform for exchange of relevant experience in selected topics including:

\begin{enumerate}
\item Outlook and Opportunities
\item Sustainable Infrastructure Development for Socio-Economic Growth
\item Investment Climate in Nepal
\item Infrastructure Financing Mechanisms
\item Enabling Policy Initiatives
\end{enumerate}

Accordingly, CNI has also been focusing on the resilience of the infrastructure of the country as the result of which CNI came out with a policy document of "Construction of Eco-Friendly Linear Infrastructure" with the assistance WWF Nepal. In nutshell, after the NIS 2014, the activities performed were:

- Formation and effective operationalization of Infrastructure Cell in CNI.
- Follow up workshops/seminars.
- Workshop on Infrastructure Financing - Opportunities and Challenges.
- Series of workshop on "Public-Private Partnerships".
- Workshop on financing of storage-based hydroelectricity projects
- Lobby on various issues:
  - Establishment of Infrastructure Development Bank.
  - Establishment of Project banks/Project Readiness.
  - Public-Private Partnership (PPP) Centre.
  - Other legal and institutional issues.

The 2nd Nepal Infrastructure Summit hosted by the Confederation of Nepalese Industries (CNI) facilitated discourse on the theme "Private Sector as indispensable Partner" for infrastructure development. The primary objective of the summit was to attract large scale private investment in areas of Nepal's core needs and strengths; forge stronger networks and alliances in the region for seamless connectivity; and raise awareness on why investment in infrastructure needs an urgent push in the country.

The summit focused on the strategic vision of the infrastructure, value proposition, competitiveness, policy particularly on land acquisition and environmental clearance; and regulatory enablers and business environment. CNI in collaboration with Idea Studio will collect various infrastructure ideas from different sectors of the communities to come up with a creative and an innovative **infrastructure** (transportation, irrigation, energy, housing, digital, etc) **ideas** to solve the existing epic infrastructure deficit and address to the possible future need for our country's development.

The Summit provided a platform for exchange of relevant experience in selected topics including:

- Infrastructure: The Big Picture
- Barriers and Constraints in attracting Private and Public Investment
- Expediting Public Private Partnership (PPP)
- Financing Resilient Infrastructure
- Successful PPP Model: Global and regional Perspective

## Awards

### Madan puraskar

Madan puraskar is a literary honor in Nepal which Madan Puraskar Guthi confers annually for an outstanding book in Nepali language published within the calendar year. It is considered the most prestigious literature award in Nepal.

It was established by daughter in law of Prime Minister Chandra Shumsher JBR Queen Jagadamba Kumari Devi, in memory of her husband late General Madan Shumsher JBR, on September 26, 1955. Since then it has been presented every year, except in 1974 and 1977. At the time of its establishment, the award prize was NRS 4000. Since the Golden Jubilee year 2005 the award prize has been increased to NRs. 400,000.

**List of winners**

```{r winners-list}
# madan_puraskar <- read_html("https://en.wikipedia.org/wiki/Madan_Puraskar") %>% 
#   html_nodes(xpath = '//*[@id="mw-content-text"]/div/table[2]')
# 
# madan_puraskar %>% 
#   .[[1]] %>%
#   html_table() %>% 
#   as_tibble() %>% 
#   write_csv("./madan_puraskar_awardees.csv", na = "")

madan_puraskar <- read_csv("./data/nepal_madan_puraskar_awardees.csv")

madan_puraskar %>% 
  knitr::kable(booktabs = TRUE, caption = "List of Madan Puraskar winners till 2075", longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped", font_size = 8) %>% 
  kableExtra::column_spec(column = 2:3, width = c("14em", "24em"))
```

### CNN heroes

```{r cnn-heroes}
tribble(~"year", ~"event", ~"hero", 
        2007, 1, "Pablo Fajardo, Ecuador",
        2008, 2, "Liz McCartney, Louisiana, US", 
        2009, 3, "Efren Penaflorida, Cavite city, Philadelphia, US", 
        2010, 4, "Anuradha Koirala, Kathmandu, Nepal", 
        2011, 5, "Robin Lim, Bali, Indonesia", 
        2012, 6, "Pushpa Basnet, Nepal", 
        2013, 7, "Chad Pregracke, US", 
        2014, 8, "Pen Farthing, UK", 
        2015, 9, "Maggie Doyne, New Jersey, US", 
        2016, 10, "Pushpa Basnet, Kathmandu, Nepal", 
        2016, 11, "Jeison Aristizabal, Cali, Columbia", 
        2017, 12, "Amy Wright", 
        2018, 13, "Ricardo Pun-Chong", 
        2019, 14, "Freweini Mebrahtu (Helped Ethiopian girls stay in school") %>% 
  knitr::kable(booktabs = TRUE, caption = "List of CNN hero award receipients", longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped") %>% 
  kableExtra::column_spec(column = 1:2, width = c("4em", "3em", "20em"))
```

## Chronology of historical events of Nepal

```{r historical-event-dates}
read_csv("./data/nepal_memorable_date_occassions.csv", skip = 1) %>% 
  knitr::kable(booktabs = TRUE, longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped", font_size = 8) %>% 
  kableExtra::column_spec(column = 1:2, width = c("26em", "6em"))
```
