# Nepal: Population, demography, conservation and geography

## Population census, 2068

```{r census-2068}
dplyr::tribble(~"Indicator", ~"Unit", ~"Value", 
               "Male", "count", 12849041,
               "Female", "count", 13645463,
               "Annual population growth rate", "percentage", 1.35,
               "Population density", "individuals per msq", 180,
               "Total engagement in agriculture", "percentage", 65.6,
               "Male engagement in agriculture", "percentage", 60.2,
               "Female engagement in agriculture", "percentage", 72.8, 
               "Crude birth rate", "per thousand", 21.8,
               "Crude death rate", "per thousand", 7.3,
               "Child death rate", "per thousand", 40.5,
               "Net fertility rate", "percentage", 2.5, 
               "Average life expectancy", "years", 66.6) %>% 
  knitr::kable(caption = "Population census, 2068 summary", booktabs = TRUE, longtable = T) %>% 
  kableExtra::kable_styling(latex_options = "striped")

```

## Indigenous groups of Nepal

The indigenous (Adibasi/janajati) groups in Nepal are defined as social groups with a social and cultural identity distinct from the dominant society. The National Foundation for Upliftment of Adivasi/Janjati Act (2002) defines those ethnic groups and communities who have their own mother language and traditional rites and customs, distinct cultural identity, distinct social structure and written or unwritten history. The Act has recognized 59 indigenous communities in Nepal. 

These groups as a whole are generally considered to be the marginalized segment of the population who engage in economic activities ranging from hunting and gathering,and shifting agriculture in or near forests, to wage laborers or even small-scale market-oriented activities. However, _Adibasi_/ _janajati_ amongst themselves are diverse groups who do not all come under one economic system.

There are disparities amongst different _Adivasi_/ _Janajati_ groups in Nepal. While Adivasi Janajati groups such as _Rautes_ are still engaged in hunting and collecting food, _Chepangsand_, _Kusundas_ practice slash and burn, shifting cultivation and depend mainly on natural resources. On the other hand, Newars, Thakalis and Gurungs are more exposed to modernity and are involved in foreign employment, government and non-government services, industry and commerce.

Considering their diverse socioeconomic status, the Nepal Federation of Indigenous Nationalities (Adivasi Janajati) (NEFIN) 2004, an umbrella organization of Adivasi Janajati groups has classified _Adivasi_ _Janajati_ groups into five categories (\ref{tab:adivasi-janajati-classification}).  Of the total 59 Adivasi Janajati groups, 10 groups are categorized as "endangered", 12 groups as “highly marginalized", 20 groups as "marginalized", 15 groups as "disadvantaged" and 2 groups as "advanced" or better off on the basis of a composite index consisting of literacy, housing, land holdings, occupation, language, education, and population size.

```{r adivasi-janajati-classification}
tribble(
  ~"region", ~"count", ~"endangered", ~"higly_marginalized", ~"marginalized", ~"disadvantaged", ~"advantaged",
  "Mountain", 18, NA, "Shiyar, Shingsawa (lhomi), and Thudam", "Bote, Dolpo, Larke, Lhopa, Mugali, Tokpegola and Walung", "Bara gaule, Byansi (Sauka), Chhaairotan, Marphali thakali, Sherpa, Tangbe and Tingaunle thakali", "Thakali",
  "Hills", 24, "Bankariya, Hayu, Kusbadiya, Kusunda, Lepcha, Surel", "Baramu, Thami (Thangmi), Chepang", "Bhujel, Dura, Pahari, Phree, Sunuwar, Tamang", "Chhantyal, Gurung (Tamu), Jirel, Limbu (Yakthumba), Magar, Rai, Yakkha, Hyolmo", "Newar",
  "Inner terai", 7, "Raji, Raute", "Bote, Danuwar, Majhi", "Darai, Kumal", NA, NA,
  "Terai", 10, "Kisan, Meche (Bodo)", "Dhanuk (Rajbansi), Jhangad, Santhal (Satar)", "Dhimal, Gangai, Rajbansi (Koch), Tajpuriya, Tharu", NA, NA
) %>% 
  rename_all(function(x)str_to_sentence(str_replace_all(x, "_", " "))) %>% 
  knitr::kable(booktabs = TRUE, caption = "Classification of Adivasi/Janajatis in Nepal; Source: NEFIN, 2004", longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped", font_size = 8) %>% 
  kableExtra::column_spec(column = 1:7, width = c("5em", "4em", rep("8em", 5)))
  
```

## Geographical and political division of Nepal

- Himalayan region 15% of land with 16 districts
- Hilly region 68% of land with 39 districts
- Terai region 17%of land with 20 districts.
- Land with the lowest altitude from sea level: Kechanakalan (Jhapa)
- Nepal covers an area of 0.03% of the world and 0.3% of Asia
- Largest district: Dolpa
- Smallest district: Bhaktapur
- Largest Lake of Nepal: Rara
- Deepest lake of Nepal: Shey - Phoksundo (Y - Shaped lake)
- The lake situated at highest altitude of the world: Tilicho (Manang)
- The total agricultural land in terai: 53% of the total
- Total national parks: 11
- Biggest national park: Shey - Phoksundo N.P. (3555 sq.km)
- Smallest national park: Rara N.P. (106 sq.km)
- First national Park: Chitwan N.P (listed in world heritage site) established in 1973 AD
- Last national park (recently established): Banke N.P.
- Langtang N.P. famous for Red Panda and Chitwan N.P. famous for One horned rhino
- Koshi Tappu Wildlife reserve famous for Wild buffalo (Arna)

**Political division and basic information**

- Total municipality in Nepal: 191
- Metropolitian Municipality: 1 (Ktm)
- Submetropolitian Municipality: 11
- Total Village Development Committee (VDC) in Nepal: 3276
- The districts without VDC: 2 (Kathmandu and Bhaktapur)
- Population of Nepal according to census 2068 BS: 26494504
- Male population 48.5% and female population 51.5%
- Population density, census 2068 BS: 180 population/sq.km
- Literacy rate, census 2068 BS: 65.9% (male: 75.1% and female: 57.4%)
- 1st president of Nepal: Dr. Ram Baran Yadav
- 1st Vice - President of Nepal: Parmananda Jha
- Present Prime Minister of Nepal: Puspa Kamal Dahal (39th Prime Minister of Nepal)
- Present Finance Minister of Nepal: Krishna Bahadur Mahara
- Present Energy Minister of Nepal: Janardan Sharma
- Present Health Minister of Nepal: Gagan Thapa
- Present Education Minister of Nepal: Dhaniram Poudel
- Present Forest Minister of Nepal àShankar Bhandari
- Present Agriculture Minister of Nepal: Gauri Shankar Chaudhary
- 1st Prime Minister of Nepal: Bhimsen Thapa
- 1st Lady Minister of Nepal: Dwarika Devi Thakurani
- 1st Census taken in Nepal: 1968 BS (1911 AD)
- 1st five year plan started in Nepal (1956-1961 AD): 2013, Asoj 01
- Districts linking both India and China: 2 (Darchula and Taplejung)
- District of Baunna Pokhari Tripanna Tal: Rukum
- Baglung district is known as district of Hanging bridges. It is the district with the boundary similar to map of Nepal.
- District of Terai not linked with Mahendra Highway: Parsa
- Famous district for production of Coffee: Gulmi
- Famous district of Orange production: Dhankuta
- Total budget allocated for Fiscal year 2072/73 BS: 8 Kharab 19 arab 64 crore and88 lakh.
- Severe earthquake on 12th Baisakh 2072 BS at 11:36 am took more than 8850 people.
- CEO of present Cricket Association Nepal: Bhawana Ghimire
- Constitution Asembly - 2 election at 2070/08/04

## Protected areas: National park, wildlife reserve and buffer zone

```{r national-parks-protected-areas}
read_csv("./data/nepal_protected_areas.csv", skip_empty_rows = TRUE) %>% 
  knitr::kable(booktabs = TRUE, caption = "List of protected areas with general information", longtable = TRUE) %>%
  # kableExtra::kable_styling(latex_options = "striped", font_size = 8) %>% 
  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::column_spec(column = 1:5, width = c("6em", "5em", "5em", "5em", "18em"))
```

## Hulaki rajmarga (Hulaki highway)

http://www.karma99.com/
http://www.karma99.com/2015/09/hulaki-rajmarga.html

