## Events and programmes

### Nepal Investment Summit

Nepal hosted 3rd edition of Nepal Investment Summit on March 29-30, 2019 in the Kathmandu in an effort to further enhance Nepal's standing as a promising investment destination and to build on the recent encouraing developments. The 2nd summit was held in 2017, while the first one was held in 1992. 

Major Outcomes of Investment Summit, 2019

- Nepal Investment Summit 2019 has reportedly witnessed signing of 15 new deals and MoUs for new projects in Nepal
- Besides, the country has also received proposals, 17 applications for 10 other projects presented as part of the Summit
- Transport, hydropower, hospital, airport, convention center and agriculture infrastructure were among areas that received investment proposals
- India, Vietnam, United States, South Korea, China, Britain were among countries that represented participating investors
- International Finance Corporation, World Bank Group, Asian Development Bank, Multilateral Investment Guarantee Agency, were among the key multilateral donor agencies entered into separate investment and cooperation deals during the summit
- One of the world's largest solar development company SkyPower announced a new partnership with Nepal's Chaudhary Group for a 600-MW capacity renewable solar energy projects.
- PM and Finance Minister Khatiwada held 30 side-line bilateral meetings with investors and delegates as part of the Summit
- More than 1300 participants and around 735 foreign delegates from more 300 companies attended the Summit


The government, in an effort to attract foreign investors, has introduced three vital legislations—Foreign Investment and Technology Transfer Act, Public-Private Partnership and Investment Act, and Special Economic Zone Act (First Amendment).

### Nepal Infrastructure Summit

Nepal Infrastructure Summit (NIS) 2014, organized by CNI in collaboration with Government of Nepal and YCNC, with the theme "Accelerating Investment in Infrastructure" was 1st ever summit organized of its kind in Nepal. The Summit was successful as it was able to deliver high attendance, important and high-rated keynote speech, excellent speakers and panelists who knew their subject, well facilitated dialogue sessions, a great venue for networking and the presence of aspiring young participants.

The Summit provided a platform for exchange of relevant experience in selected topics including:

\begin{enumerate}
\item Outlook and Opportunities
\item Sustainable Infrastructure Development for Socio-Economic Growth
\item Investment Climate in Nepal
\item Infrastructure Financing Mechanisms
\item Enabling Policy Initiatives
\end{enumerate}

Accordingly, CNI has also been focusing on the resilience of the infrastructure of the country as the result of which CNI came out with a policy document of "Construction of Eco-Friendly Linear Infrastructure" with the assistance WWF Nepal. In nutshell, after the NIS 2014, the activities performed were:

- Formation and effective operationalization of Infrastructure Cell in CNI.
- Follow up workshops/seminars.
- Workshop on Infrastructure Financing - Opportunities and Challenges.
- Series of workshop on "Public-Private Partnerships".
- Workshop on financing of storage-based hydroelectricity projects
- Lobby on various issues:
  - Establishment of Infrastructure Development Bank.
  - Establishment of Project banks/Project Readiness.
  - Public-Private Partnership (PPP) Centre.
  - Other legal and institutional issues.

The 2nd Nepal Infrastructure Summit hosted by the Confederation of Nepalese Industries (CNI) facilitated discourse on the theme "Private Sector as indispensable Partner" for infrastructure development. The primary objective of the summit was to attract large scale private investment in areas of Nepal's core needs and strengths; forge stronger networks and alliances in the region for seamless connectivity; and raise awareness on why investment in infrastructure needs an urgent push in the country.

The summit focused on the strategic vision of the infrastructure, value proposition, competitiveness, policy particularly on land acquisition and environmental clearance; and regulatory enablers and business environment. CNI in collaboration with Idea Studio will collect various infrastructure ideas from different sectors of the communities to come up with a creative and an innovative **infrastructure** (transportation, irrigation, energy, housing, digital, etc) **ideas** to solve the existing epic infrastructure deficit and address to the possible future need for our country's development.

The Summit provided a platform for exchange of relevant experience in selected topics including:

- Infrastructure: The Big Picture
- Barriers and Constraints in attracting Private and Public Investment
- Expediting Public Private Partnership (PPP)
- Financing Resilient Infrastructure
- Successful PPP Model: Global and regional Perspective

## Awards

### National

#### Madan puraskar

Madan puraskar is a literary honor in Nepal which Madan Puraskar Guthi confers annually for an outstanding book in Nepali language published within the calendar year. It is considered the most prestigious literature award in Nepal.

It was established by daughter in law of Prime Minister Chandra Shumsher JBR Queen Jagadamba Kumari Devi, in memory of her husband late General Madan Shumsher JBR, on September 26, 1955. Since then it has been presented every year, except in 1974 and 1977. At the time of its establishment, the award prize was NRS 4000. Since the Golden Jubilee year 2005 the award prize has been increased to NRs. 400,000.

**List of winners**

```{r winners-list}
# madan_puraskar <- read_html("https://en.wikipedia.org/wiki/Madan_Puraskar") %>% 
#   html_nodes(xpath = '//*[@id="mw-content-text"]/div/table[2]')
# 
# madan_puraskar %>% 
#   .[[1]] %>%
#   html_table() %>% 
#   as_tibble() %>% 
#   write_csv("./madan_puraskar_awardees.csv", na = "")

madan_puraskar <- read_csv("./data/nepal_madan_puraskar_awardees.csv")

madan_puraskar %>% 
  knitr::kable(booktabs = TRUE, caption = "List of Madan Puraskar winners till 2075", longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped", font_size = 8) %>% 
  kableExtra::column_spec(column = 2:3, width = c("14em", "24em"))
```

**CNN heroes**

```{r cnn-heroes}
tribble(~"year", ~"event", ~"hero", 
        2007, 1, "Pablo Fajardo, Ecuador",
        2008, 2, "Liz McCartney, Louisiana, US", 
        2009, 3, "Efren Penaflorida, Cavite city, Philadelphia, US", 
        2010, 4, "Anuradha Koirala, Kathmandu, Nepal", 
        2011, 5, "Robin Lim, Bali, Indonesia", 
        2012, 6, "Pushpa Basnet, Nepal", 
        2013, 7, "Chad Pregracke, US", 
        2014, 8, "Pen Farthing, UK", 
        2015, 9, "Maggie Doyne, New Jersey, US", 
        2016, 10, "Pushpa Basnet, Kathmandu, Nepal", 
        2016, 11, "Jeison Aristizabal, Cali, Columbia", 
        2017, 12, "Amy Wright", 
        2018, 13, "Ricardo Pun-Chong", 
        2019, 14, "Freweini Mebrahtu (Helped Ethiopian girls stay in school") %>% 
  knitr::kable(booktabs = TRUE, caption = "List of CNN hero award receipients", longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped") %>% 
  kableExtra::column_spec(column = 1:2, width = c("4em", "3em", "20em"))
```
