# General knowledge objective

## Environment, conservation and biodiversity

**Protected areas: National park, wildlife reserve and buffer zone**

```{r national-parks-protected-areas}
read_csv("./data/nepal_protected_areas.csv", skip_empty_rows = TRUE) %>% 
  knitr::kable(booktabs = TRUE, caption = "List of protected areas with general information", longtable = TRUE) %>%
  kableExtra::kable_styling(latex_options = "striped", font_size = 8) %>% 
  kableExtra::column_spec(column = 1:5, width = c("6em", "5em", "5em", "5em", "18em"))
```

## Days, year, decades and national and international observances

**Day observances**

```{r day-observances}
# retrieved: April 6, 2020
# read_html("https://en.wikipedia.org/wiki/List_of_minor_secular_observances") %>% 
#   html_table(fill = T) %>% 
#   .[3:(3+11)] %>% 
#   map_dfr(function(x)as_tibble(x, .name_repair = "universal")) %>% 
#   write_csv("./data/minor_secular_observances_international_days.csv", na = "")

# todo: remove square bracket citations
read_csv("./data/world_minor_secular_observances_international_days.csv") %>% 
  mutate_all(list(~str_remove_all(., pattern = "\\[\\d*\\]"))) %>%
  knitr::kable(booktabs = TRUE, caption = "List of minor secular observances (Days)", longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped") %>%
  kableExtra::column_spec(column = 1:3, width = c("8em", "18em", "10em"))
```

**International year observances**

```{r international-years}
# retrieved: April 6, 2020
read_csv("./data/world_minor_secular_observances_international_year.csv") %>% 
  mutate_all(list(~str_remove_all(., pattern = "\\[\\d*\\]"))) %>%
  knitr::kable(booktabs = TRUE, caption = "List of minor secular observances (Years)", longtable = TRUE) %>% 
  kableExtra::kable_styling(latex_options = "striped") %>% 
  kableExtra::column_spec(column = 1:2, width = c("8em", "22em"))

```

**Decade observances**

```{r international-decades}
# retrieved: April 6, 2020
read_csv("./data/world_minor_secular_observances_international_decades.csv") %>% 
  mutate_all(list(~str_remove_all(., pattern = "\\[\\d*\\]"))) %>%
  knitr::kable(booktabs = TRUE, caption = "List of minor secular observances (Decades)", longtable = TRUE) %>%
  kableExtra::kable_styling(latex_options = "striped") %>% 
  kableExtra::column_spec(column = 1:3, width = c("8em", "20em", "10em"))

```

**Other observances**

- Greenery Day -- May 4
- Remembrance of the Dead -- May 4
- World Wide Day of Genital Autonomy -- May 7
- Teacher's Day -- May 8
- Victory in Europe Day -- May 8
- Military Spouse Day -- May 11
- Mother's Day -- May 13
- International Day of Families -- May 15
- Norwegian Constitution Day -- May 17
- World Inflammatory Bowel Disease (IBD) Day - May 19
- Labour Day (Jamaica) -- May 23
- World Orienteering Day -- May 24
- African Liberation Day -- May 25
- International Missing Children's Day -- May 25
- World Multiple Sclerosis Day -- May 25
- Menstrual Hygiene Day -- May 28
- Memorial Day -- last Monday of May

- Queen's Official Birthday -- first, second or third Saturday in June
- National Cancer Survivors Day (US) -- first Sunday of June
- Republic Day (Italy) -- June 2
- Danish Constitution Day -- June 5
- Coral Triangle Day -- June 9
- Independence Day (Philippines) -- June 12
- Juneteenth -- June 19 and/or third Saturday of the month
- World Hydrography Day -- June 21
- World Music Day -- June 21
- Fête Nationale du Québec -- June 24
- Tau Day -- June 28
- World Wide Knit in Public Day -- second Saturday in June

- National Doctors' Day (India) -- July 1
- Chartered Accountants' Day (India) -- July 1
- Tynwald Day (Isle of Man) -- July 5
- The Twelfth (Northern Ireland) -- July 12
- Kargil Vijay Diwas -- July 26
- Comic Sans Day - First Friday of July

- International Beer Day -- first Friday of August
- Emancipation Day (Jamaica) -- August 1
- Yorkshire Day -- August 1
- Friendship Day -- first Sunday of August
- Independence Day (Jamaica) -- August 6
- National Day (Singapore) -- August 9
- International Youth Day -- August 12
- International Lefthanders Day -- August 13
- Youm-e-Azadi (Pakistan Independence Day) -- August 14
- National day of mourning (Bangladesh) -- August 15
- Independence Day (India) -- August 15
- Victory over Japan Day (UK) -- August 15
- Bennington Battle Day -- August 16
- Indonesian Independence Day -- August 17
- World Mosquito Day -- August 20
- Indian Akshay Urja Day -- August 20
- International Day for the Remembrance of the Slave Trade and its Abolition -- August 23
- European Day of Remembrance for Victims of Stalinism and Nazism -- August 23
- Women's Equality Day -- August 26
- National Sports Day -- August 29
- Hari Merdeka (Malaysia Independence Day) -- August 31
- Friendship Day -- First Sunday of August

- Victory over Japan Day (US) -- September 2
- Skyscraper Day -- September 3
- Teachers' Day (India) -- September 5
- Defense Day (Pakistan) -- September 6
- Brazilian Independence Day -- September 7
- World Physical Therapy Day -- September 8
- Patriot Day -- September 11
- Onam (Kerala, India) -- September 4, 2017
- Hindi Day -- September 14
- Engineer's Day (India) -- September 15
- Start of Mexican Independence Day -- September 16
- Malaysia Day -- September 16
- World Car Free Day -- September 22
- Heritage Day (South Africa) -- September 24
- Botswana Day -- September 30
    
- World Habitat Day -- first Monday of October
- World Ballet Day -- a day in the first week of October
- World Sight Day -- second Thursday of October
- International Day of Older Persons -- October 1
- International Coffee Day -- October 1
- World Vegetarian Day -- October 1
- Gandhi Jayanthi -- October 2
- International Day of Non-Violence -- October 2
- German Unity Day -- October 3
- Stevie Ray Vaughan Day (Austin, Texas, US) -- October 3
- World Animal Day -- October 4
- World Teachers' Day -- October 5
- German-American Day -- October 6
- National Poetry Day (Britain) -- October 6
- World Post Day -- October 9
- World Mental Health Day -- October 10
- Fiji Day (Fiji) - October 10
- Coming Out Day -- October 11
- Fiesta Nacional de España -- October 12
- World Standards Day -- October 14
- Pregnancy and Infant Loss Remembrance Day -- October 15
- Global Handwashing Day -- October 15
- World Students' Day -- October 15
- World Food Day -- October 16
- International Day for the Eradication of Poverty -- October 17
- World Osteoporosis Day -- October 20
- Trafalgar Day (United Kingdom) -- October 21
- Mole Day -- October 23
- United Nations Day -- October 24
- Intersex Awareness Day -- October 26
- Labour Day (New Zealand) -- fourth Monday in October
- National Cat Day (US) -- October 29
- Halloween -- October 31
- Reformation Day -- October 31
- World Ballet Day -- a day during the first week in October
    
- Kerala Piravi -- November 1
- World Vegan Day -- November 1
- All Saints' Day -- November 1
- All Souls' Day -- November 2
- Guy Fawkes Day -- November 5
- Intersex Day of Remembrance -- November 8
- Iqbal Day -- November 9
- Armistice Day (also Remembrance Day) -- November 11
- National Independence Day (Poland) -- November 11
- World Pneumonia Day -- November 12
- World Kindness Day -- November 13
- World Diabetes Day -- November 14
- Children's Day (some countries) -- November 14
- International Day for Tolerance -- November 16
- World Prematurity Day -- November 17
- International Men's Day -- November 19
- World Toilet Day -- November 19
- Citizen's Day -- November 19
- Universal Children's Day -- November 20
- Transgender Day of Remembrance -- November 20
- World Television Day -- November 21
- Thanksgiving -- November 23
- International Day for the Elimination of Violence against Women -- November 25
- Law Day (India) -- November 26
- National Milk Day (India) -- November 26
- Constitution Day (India) -- November 26
- Cities for Life Day -- November 30
- World Philosophy Day -- third Thursday in November

- International Volunteer Day -- December 5
- Sinterklaas -- December 5 / 6
- Independence Day (Finland) -- December 6
- Feast of the Immaculate Conception -- December 8
- Bahrain National Day -- December 16
- International Tea Day -- December 15
- Day of Reconciliation -- December 16
- International Day to End Violence Against Sex Workers - December 17
- Christmas Eve -- December 24
- Christmas Day -- December 25
- Good Governance Day (India) -- December 25
- Quaid-e-Azam Day -- December 25
- Boxing Day -- December 26
- Kwanzaa -- December 26 to January 1
- Benazir Bhutto Memorial Day (Karachi, Pakistan) -- December 27
- New Year's Eve -- December 31
- Purnima Sukla Paksha -- full moon day -- December

**Some important days for Nepal**

- Loktantra Day: Baisakh 11
- Ganatantra Day: Jestha 15
- NARC Day: May 8
- National Rice Day: Ashad 15
- Cooperative Day: Chaitra 20
